---
title: "Queller-Phil-ADA-homework-1"
author: "Phil Queller"
date: "2/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## homework 1

# challenge 1

```{r}
library(stringr)

quote <- gsub("[[:punct:]]","","There is grandeur in this view of life, with its several powers, having been originally breathed by the Creator into a few forms or into one; and that, whilst this planet has gone circling on according to the fixed law of gravity, from so simple a beginning endless forms most beautiful and most wonderful have been, and are being evolved")

quote





split_quote <- str_split(quote, " ")[[1]]
split_quote

every_fourth <- split_quote[seq(from = 4, to = 60, by = 4)]
every_fourth

split_quote <- sort(every_fourth, decreasing = TRUE)



```
###CHALLENGE 2:

    Create a 8 row by 10 column matrix, named m1, consisting of odd integers from 1 to 159. Fill your matrix column-wise.

    Using single bracket notation, extract and print the element in row 5, column 2.

    Using single bracket notation, extract and print the contents of rows 5 to 7 of the matrix.

    Using single bracket notation, extract the contents of (row 3, column 4) to (row 6, column 9) as a new variable, m2. What is the class of this variable? What is the mode of this variable?

```{r}

m1 <- matrix(
  data = seq(from = 1, to = 159, by = 2),
  nrow = 8,
  ncol = 10
)
m1

m1[5,2]
m1[5:7, ]

m3 <- m1[3:6,4:9]
class(m3)
mode(m3)


```

CHALLENGE 3:

    Construct a 4-dimensional, 400-element array (5 x 5 x 4 x 4), named a, consisting of the numbers 400 to 1 (i.e., a descending series)

    Given this matrix, what would the following return?
        a[1, 1, 1, 2]
        a[2, 3, 2, ]
        a[1:5, 1:5, 3, 3]

```{r}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a

a[1, 1, 1, 2]
a[2, 3, 2, ]
        a[1:5, 1:5, 3, 3]

```

Order: Primates

    Suborder: Strepsirhini
        Infraorder: Lorisiformes
            Superfamily Lorisoidea
                Family: Lorisidae
                Family: Galagidae
        Infraorder: Lemuriformes
            Superfamily Lemuroidea
                Family: Cheirogaleidae
                Family: Lepilemuridae
                Family: Indriidae
                Family: Lemuridae
                Family: Daubentoniidae
    Suborder: Haplorhini
        Infraorder: Tarsiiformes
            Superfamily Tarsioidea
                Family: Tarsiidae
        Infraorder: Simiiformes
            Parvorder: Platyrrhini
                Superfamily Ceboidea
                    Family: Cebidae
                    Family: Atelidae
                    Family: Pitheciidae
            Parvorder: Catarrhini
                Superfamily: Hominoidea
                    Family: Hylobatidae
                    Family: Hominidae
                Superfamily: Cercopithecoidea
                    Family: Cercopithecidae
```{r}
#superfamily
Lorisoidea <- c("Lorisidae","Galagidae")
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Tarsioidea <- c("Tarsiidae")
Ceboidea <- c("Cebidae", "Atelidae", "Pitheciidae")
Hominoidea <- c("Hylobatidae", "Hominidae")
Cercopithecoidea <- c("Cercopithecidae")

#parvorder
Platyrrhinni <- list("Superfamily Ceboidea" = Ceboidea)
Catarrhini <- list("Superfamily Hominoidea" = Hominoidea, "Superfamily Cercopithecoidea" = Cercopithecoidea)


#infraorder
Lorisiformes <- list("Superfamily Lorisoidea" = Lorisoidea)
Lemuriformes <- list("Superfamily Lemuroidea" = Lemuroidea)
Tarsiiformes <- list("Superfamily Tarsioidea" = Tarsioidea)
Simiiformes <- list("Superfamily Simiiformes" = Ceboidea)

#suborder
Strepsirhini <- list("Infraorder Lorisiformes" = Lorisiformes, "Infraorder Lemuriformes" = Lemuriformes)
Haplorhini <- list("Infraorder Tarsiiformes" = Tarsiiformes, "Infraorder Simiiformes" = Simiiformes)

#Order
Primates <- list("Suborder Strepsirhini" = Strepsirhini, "Suborder Haplorhini" = Haplorhini)

Primates_taxonomy <- list("Order Primates" = Primates)
Primates_taxonomy
               
```
